Data exploration

### 2021-07-09 ms/data_exploration.Rmd
Fix using biodiv_ferns_spatial with area in data_exploration.Rmd

```{r load-data}
# Load the data from the targets workflow
tar_load(biodiv_ferns_spatial)
tar_load(resp_vars_env)
tar_load(indep_vars)
tar_load(lat_area_ja)

# Make biodiversity metrics dataframe with centroid of each site for models
  biodiv_ferns_cent <- sf_to_centroids(biodiv_ferns_spatial) %>%
    # add area
    add_roll_area(lat_area_ja) %>%
    # keep only variables needed for model and only rows with zero missing data
    filter_data_for_model(c("grids", "lat", "long", resp_vars_env, indep_vars))
```

>>>>

```{r load-data}
# Load the data from the targets workflow
tar_load(biodiv_ferns_spatial)
tar_load(resp_vars_env)
tar_load(indep_vars)

# Make biodiversity metrics dataframe with centroid of each site for models
  biodiv_ferns_cent <- 
    biodiv_ferns_spatial %>%
    # keep only variables needed for model and only rows with zero missing data
    filter_data_for_model(c("grids", "lat", "long", resp_vars_env, indep_vars)) %>%
    sf::st_set_geometry(NULL) %>%
    as_tibble()
```
